Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/evaluation.tex
more ediiiiiiiitsssss

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The data center operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{x}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated. For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.

>>>>

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The data center operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated. For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.

### 2016-01-29 paper/propane.tex
more space savings
more ediiiiiiiitsssss

Policies for (distributed) control planes differ from data-plane
policies~\cite{x,y,z} in a few important ways. First, control-plane
policies must account for all failures at specification time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on topology.
%

In the rest of this section, we define \sysname policies for the two 
examples described in the previous section, introducing key aspects of
the \sysname language along the way.  The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in the next section.

@@

\begin{code}
\Define Routing = \{
     PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
that connections to the customer through both routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network and the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

@@

\begin{code}
\Define Ownership = \{
    PG1 \Path \End(A)
    PG2 \Path \End(B)
    PL1 \Path \End(E)
    PL2 \Path \End(F)
\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
For the second constraint, we can define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Routing = \{
    PG1 \OR PG2 \Path \Any
    PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
    \True      \Path \Exit(\Out)
\}
\end{code}
\noindent
The first line states that there is no restriction (\Any)
on how traffic must
traverse the network for global prefixes, aside from the default restriction
that traffic must not pass through the user's network and then loop
back on itself. This means traffic for
\CD{PG*} may be sent either from other routers in the data center, or
from external ASes. The second line ensures that traffic for local
prefixes never enters the network from an outside location. This constraint
guarantees that the services remain reachable only to locations
internal to the data center.

>>>>

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, control-plane
policies must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on topology.
%

In the rest of this section, we define \sysname policies for the two 
examples from the previous section, introducing key aspects of
the \sysname language along the way. The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in the next section.

@@

\begin{code}
\Define Routing = 
    \{PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
that connections to the customer through both routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network and the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

@@

\begin{code}
\Define Ownership = 
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
For the second constraint, we can define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Routing = 
    \{PG1 \OR PG2 \Path \Any
     PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
     \True      \Path \Exit(\Out)\}
\end{code}
\noindent
The first line states that there is no restriction (\Any)
on how traffic must
traverse the network for global prefixes, aside from the default restriction
that traffic must not pass through the user's network and then loop
back on itself. This means traffic for
\CD{PG*} may be sent either from other routers in the data center, or
from external ASes. The second line ensures that traffic for local
prefixes never enters the network from an outside location. This constraint
guarantees that the services remain reachable only to locations
internal to the data center.
